\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Generally, people find it very difficulty to schedules their rides because of the way they move from one place to another, and students suffer from this the most  especially since the travelling among cities in private cab services is not that great. As students, we think there should exist more suitable travelling solutions to places where transportation networks are efficient and cost effective and helpful for students. This  project  aims to provide a  platform  for students to improve student  mobility  via carpooling allowing vehicle owning students to share their vehicle with non vehicle owning students. Ride sharing could also be one among the simplest solutions when there's no other  mean  of  transportation  to a  particular location. \\

Mobile applications are playing a vital role in everyone’s  lives. Multiple ride sharing services with different features compete with existing transportation facilities. Some people prefer new transportation services over the  traditional services like  private cab  services. Our application "CarPool"  aims  to  promote  carpooling  by  targeting  only students, making it easier for them to stick and use this application.  To place the ride sharing system in place, we have designed and developed an android application with backend servers for users  to  access  the ride sharing service through their smartphones. Additionally, our application  involves  some  features  that  are  critical to the service. By using android development tools and libraries and efficient backend solutions, we have managed to create the application simple but powerful as well, which makes this application very useful for the students. \\ 

Our app, CarPool, will be a unique ride sharing application that would take benefits of the advantages of carpooling and try to improve and eliminate the disadvantages while focusing on making it a good carpooling experience for students. In this report, we will go through the conceptual phase and the development phase since making developing a good application requires good planning first. We describe the software development architecture supported by web services. The framework uses the three-layer architecture of web development into mobile software development. 