\chapter{Interviews} \label{ap:Appendix1}

The interviewees were three students from different departments of Air University.\\~\\
(Note : Q\&A with no recording, as we believe recording would make interviewees uncomfortable.)\\

{\textbf{Student 1 }}
\\ Name : Hassan Siddiqui 
\\ Age : 21 
\\ Gender : Male
\\ Interview date : 10.02.2020 
\\ Duration of interview : 10 minutes 
\\ Place of interview : AUSOM building 
\\ Notes from interview : The interviewee owns a Samsng Galaxy S9 smart phone which runs android 9.0. He is not familiar with concept of programming for mobile devices but he believes that, CarPool is a very interesting concept. Hassan believes that our app is very handy and he would like to install the prototype of application, on his smart phone and become one of our test user. The interviewee would like easier access to travel to and from university. He believes that, it's not easy to find out local transportation. He also mentioned that he would be happier, that he can share his ride expense and cut his fuel bills. \\

{\textbf{Student 2 }}
\\ Name : Ahmed Shahid
\\ Age : 29 
\\ Gender : Male
\\ Interview date : 10.02.2020 
\\ Duration of interview : 8 minutes 
\\ Place of interview : Department of Mechatronics
\\ Notes from interview : The interviewee owns a IPhone 7 smart phone which runs IOS. He is not familiar with concept of programming for mobile devices but he believes that, it is a very interesting concept. Ahmed believes our app is very useful and he wishes a similar application for iPhone. The interviewee would like to use this application through his Iphone. He would like to share ride with non-vehicle owning students.\\

{\textbf{Student 3}} 
\\ Nickname : Amna Asim 
\\ Age : 19 
\\ Gender : Female 
\\ Interview date : 10.02.2020 
\\ Place of interview : Department of Electrical Engineering
\\ Duration of interview : 5 minutes 
\\ Notes from interview : The interviewee owns a Oppo K1 smart phone which runs Android 8.1. She is not familiar with concept of programming for mobile devices and she believes that, it is a very interesting concept and finally someone is doing this for students. She complained a lot about the local transportation in Islamabad, which frustrate her every time, when she wants to travel to and from university. She also believes that it is a good idea to share ride with non-vehicle owning students. She also mentioned to include the feature which facilitates female students to share ride with only female students.
 