\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
In general, people have a hard time conciliating their schedules because of the way they move from one location to another.  and students suffer from this the most  especially  since transportation between cities is not that great,  As students, we think there should exist more suitable transportation solutions to places where transportation networks are short and cheap and helpful for students.
\\ This  report  proposes  a  platform  to  help  improve students  mobility  through carpooling, a way for vehicle owning students to share their private vehicle with non vehicle owning students in order to splitting and reducing costs. carpooling may be one of the best solutions when there is no other  mean  of  transportation  to a  specific location  but naturally  it  is not  the  only one. Mobile  applications  take more  and more  part of  everyone’s  lives, different  services for carpooling with different features begin to compete with existing transportation solutions. Some people start to  prefer using  new carpooling  services  over the  traditional services represented  by  taxi  services. CarPool  aims  to  promote  carpooling  by  targeting  students making it easier for them to adhere and use this system.  By  targeting  students  people  will  more  likely  join  the  service  since  its  users  are primarily other people form the same environment. to put the carpooling system in place, we have designed and developed an Android mobile application with backend servers for users  to  access  the  carpooling  service  through  their  smartphones,  additionally  the application  involves  some  features  that  are  critical  to  the  service.  by  using  Android Development  Tools  and  Libraries and  efficient backend  solutions  we  have managed  to make the application simple but powerful as well, which makes this application very useful for the students to use.
\\ The combination of the smart phone and the Internet service is the trend of the future information development and software applications. Mobile phones are the most commonly used communication tools. Using mobile phones to obtain information is not only quick, but also more convenient shortcut to improve people's lives. in the paper, we propose the software development architecture based on Web services. This framework introduces the three-layer architecture of Web development into mobile phone software development. based on the threelayer architecture, the android based CarPool system is developed.
\\ Our app CarPool will be a unique carpooling application that would take benefits of the advantages of carpooling and try to improve and eliminate the disadvantages, all while focusing on making it a good carpooling experience for students. the realization of our project will go through the conceptual phase and then development phase. since making a good application requires good planning first.