\chapter{Interviews} \label{ap:Appendix1}

\section*{}
The interviewees were three students from different departments of Air University.\\~\\
\large {\textbf{Student 1 }}
\\ Name : Hassan Siddiqui 
\\ Age : 21 
\\ Sex : Male
\\ Interview date : 10.02.2020 
\\ Duration of interview : 10 minutes 
\\ Place of interview : AUSOM building 
\\ Method : Note taking and no recording as we believe recording would make interviewees uncomfortable.
\\ Notes from interview : The interviewee owns a Samsng Galaxy S9 smart-phone which runs android 9.0, he is not familiar with concept of programming for mobile devices but he believes it is a very interesting concept. Hassan believes our app is very handy and he would even liked to install our prototype, on his own smart-phone and become one of our test users. the interviewee would like easier access to travel to and from university he believes it is not easy to find out local transportation. he mentioned that he would be even happier that he can share their ride expenses and cut their fuel bills.\newpage
\large {\textbf{Student 2 }}
\\ Name : Ahmed Shahid
\\ Age : 29 
\\ Sex : Male
\\ Interview date : 10.02.2020 
\\ Duration of interview : 8 minutes 
\\ Place of interview : Department of Mechatronics
\\ Method : Note taking and no recording as we believe recording would make interviewees uncomfortable. \\\ Notes from interview : The interviewee owns a iPhone 7 smart-phone which runs IOS. he is not familiar with concept of programming for mobile devices but he believes it is a very interesting concept. Ahmed believes our app is very useful and he wishes a similar application for iPhone. The interviewee would like to use this application through cell phone, or his future iPad. he specially would like to share ride with non-vehicle owning students.\\~\\
\large{\textbf{Student 3}} 
\\ Nickname : Amna Asim 
\\ Age : 19 
\\ Sex : Female 
\\ Interview date : 10.02.2020 
\\ Place of interview : Department of Electrical Engineering
\\ Duration of interview : 5 minutes 
\\ Method : Note taking and no recording as we believe recording would make interviewees uncomfortable.
\\ Notes from interview : The interviewee owns a Oppo K1 smart-phone which runs Android 8.1. she is not familiar with concept of programming for mobile devices and she believes it is a very interesting that someone finally is doing this for students. she complained a lot about the local transportation in Islamabad which frustrate her every time she wants to travel to and from university. she believes also that it is a good idea to share ride with other non-vehicle owning students. she also mention that include the feature that facilitate female students to share ride with only female students.
 