\chapter{Literature Review} \label{chap:literatureReview}

\section*{Carpooling}

\section{Definition and general principle}
\justify
Carpooling (also car-sharing, ride-sharing and lift-sharing) is the sharing of car journeys so that more than one person travels in a car, and prevents the need for others to have to drive to a location themselves.
\\ By having more people using one vehicle, carpooling reduces each person's travel costs 
such as: fuel costs, tolls, and the stress of driving. carpooling is also a more environmentally 
friendly and sustainable way to travel as sharing journeys reduces air pollution, carbon emissions, traffic congestion on the roads, and the need for parking spaces. authorities often encourage carpooling, especially during periods of high pollution or high fuel prices. car sharing is a good way to use up the full seating capacity of a car, which would otherwise remain unused if it were just the driver using the car.
\\ In 2009, carpooling represented 43.5\% of all trips in the United States and 10\% of commute trips. the majority of carpool commutes (over 60\%) are "fam-pools" with family members.
\\ Carpool commuting is more popular for people who work in places with more jobs 
nearby, and who live in places with higher residential densities. carpooling is significantly correlated with transport operating costs, including fuel prices and commute length, and with measures of social capital, such as time spent with others, time spent eating and drinking and being unmarried. however, carpooling is significantly less likely among people who spend more time at work, elderly people, and homeowners.
\\ Carpooling usually means to divide the travel expenses equally between all the 
occupants of the vehicle (driver or passenger). the driver does not try to earn money, but 
to share with several people the cost of a trip he would do anyway. the expenses to be divided basically include the fuel and possible tolls. But if we include in the calculation the depreciation of the vehicle purchase and maintenance, insurance and taxes paid by the driver, we get a cost around 20RS/km. There are platforms that facilitate carpooling by connecting people seeking respectively passengers and drivers. usually there is a fare set up by the car driver and accepted by passengers because they get an agreement before trip start.

\section{Carpooling Types}
\subsection{Regular}
The car is often perceived as an extension of the personal space, the driver, alone in his vehicle is in a closed space; he is free to do what he likes: listen to the radio, sing, call with headsets etc. carpooling regularly is to share a dialogue, experiences, stories. in the United States an intermediate concept has developed between carpooling and the public transport line: the vanpool. These are minibuses chartered by an employer, a public authority or a private company and made available to a group of people who regularly make the same journey.

\subsection{Occasional}
This type of carpooling is mainly used for leisure or last minute departures. the linking is often done through websites or mobile applications, which can significantly reduce travel costs, but usually requires to carpool with one or more unknown.
this type of carpooling is mainly used for leisure or last minute departures. the linking is often done through websites or mobile applications, which can significantly reduce travel costs, but usually requires to carpool with one or more unknown.

\subsection{Eventual}
Participants in an event (music festival, sporting event, wedding, associative or 
institutional meeting ...) can organize to carpool to the venue of the event. this one-time carpool has a special feature: all participants travel to the same place on the same date.carpooling is also used for departures on holidays or weekends, savings on a trip being even larger than the trip is long. So carpooling becomes an alternative of affordable and accessible transportation.
\\ There are also "cultural" carpooling platforms to visit a cultural site: castles, 
museums, exhibitions, artists' studios, religious places, festivals, etc.
\section{Advantages and disadvantages of carpooling applications}
\subsection{Advantages of carpooling}
\begin{itemize}
\item The main advantage of rideshare solutions is cost saving, of course. depending on the agreement, a ride can be twice as cheap than traveling by conventional way.
\item The car is not a gas cost only. there are some cost items for the maintenance, repair, parts replacement in your vehicle. If you reduce the time of car utilization, you reduce these costs.
\item A fewer number of cars on the road can reduce the CO2 emission in the roads and make the air we breathe cleaner. 
\item Saving time. fewer cars - fewer traffic jams. that is to say, it is possible to reach a destination point faster and find a parking place.
\item Meeting new people. traveling together allows you to find good friends. 
\end{itemize}

\subsection{Disadvantages of carpooling}
\begin{itemize}
\item Indecent passengers. some people can try to discount the price or even ask the driver to visit the place that is not on the scheduled route. and it is important to screen out such individuals at the very beginning of traveling. 
\item Indecent drivers. unfortunately, some drivers can play an unfair game as well. for example, drivers who take 5-6 people in a small car and ask for a high price. 
\item In some cases, a driver has to pick up each companion separately. it increases the time of traveling.
\item Passengers can be not satisfied with the driving style of a car owner. in turn, the driver can be annoyed with an excessive volubility of companions, their untidiness or lack of manners
\end{itemize}